Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks

### 2017-11-16 papers/cvpr2018/2_method.tex
Another pass.

There are two types of errors that can occur in connectomics segmentation.
The first, called a split error, occurs when there are two segments that should have been merged. The second, called a merge error, happens when one segment should be split into two. Generally, it is much more difficult to correct merge errors than to correct split errors,
as the space of possible split proposals grow quickly~\cite{parag2015properties}.
Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pipelines (Sec.~\ref{sec:neuroproof}). Our goal is to identify locations of split errors and merge the corresponding segments automatically.

@@

A typical approach to generating edges produces an edge between all adjacent segments. Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
However, this method produces too many edges in the graph for graph-based optimization approaches. We identify a smaller number of pairs of segments to consider as graph edges using the following approach.

>>>>

There are two types of errors that can occur in connectomics segmentation.
The first, called a split error, occurs when there are two segments that should have been merged. The second, called a merge error, happens when one segment should be split into two. Generally, it is much more difficult to correct merge errors than to correct split errors,
as the space of possible split proposals grows quickly~\cite{parag2015properties}.
Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pipelines (Sec.~\ref{sec:neuroproof}). Our goal is to identify locations of split errors and merge the corresponding segments automatically.

@@

A typical approach for generating edges produces one between all adjacent segments. Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
However, this method produces too many edges in the graph for graph-based optimization approaches. We identify a smaller number of pairs of segments to consider as graph edges using the following approach.

### 2017-11-16 papers/cvpr2018/3_evaluation.tex
Another pass.

We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from two different animals.

@@

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}. The mushroom body in this species is the major site of associative learning. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $1000 \times 1000 \times 1000$ voxels.

@@

The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.

@@

The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. Ideally, the merge candidates output by this algorithm will contains all possible positive examples with a very limited number of negative examples. After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produce the best results considering this objective.

In our implementation we use nanometers for these thresholds and not voxels. Connectomics datasets often have lower sample resolutions in $z$. Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime. For example, the thresholds in voxels are $t_{low} = (40, 40, 8)$ and $t_{high} = (100, 100, 20)$ for the anisotropic Kasthuri dataset and $t_{low} = (24, 24, 24)$ and $t_{high} = (60, 60, 60)$ for the isotropic FlyEM dataset.

>>>>

We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from two different species.

@@

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}. The mushroom body in this species is the major site of associative learning. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $1000 \times 1000 \times 1000$ voxels.

@@

The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.

@@

The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. Ideally, the merge candidates output by this algorithm will contain all possible positive examples with a very limited number of negative examples. After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produce the best results considering this objective.

In our implementation we use nanometers for these thresholds and not voxels. Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime. For example, the thresholds in voxels are $t_{low} = (40, 40, 8)$ and $t_{high} = (100, 100, 20)$ for the anisotropic Kasthuri dataset and $t_{low} = (24, 24, 24)$ and $t_{high} = (60, 60, 60)$ for the isotropic FlyEM dataset.

### 2017-11-16 papers/cvpr2018/4_results.tex
paper: changed location of table
Another pass.

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-train-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-test-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth.}
	\label{fig:variation-of-information}
\end{figure*}

@@

We evaluate the performance of the different methods using the split version of variance of information (VI)~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over and undersegmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively. Since we are measuring the entropy between two clusterings, better VI scores are closer to the origin.

@@

Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \FIX{X\%} and only increasing the VI merge score by \FIX{X\%}.
Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
We see significant improvements on the Kasthuri datasets (VI split reduction of \FIX{X\%} and \FIX{X\%} on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \FIX{X\%} and \FIX{X\%}). This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. It is well known that isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.

Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol. 2 dataset. Several of these examples combine multiple consecutive segments that span the volume.
In the third example we correct the over-segmentation of a dendrite.
Fig.~\ref{fig:negative-results} shows some failure cases (red circles)
In two of these examples the algorithm correctly predicted several merges but made one error.
In the third example (blue circle) a merge error in the initial segmentation propagated to our output.
We now analyze how each major component of our method contributes to this final result.

@@

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause a break in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:positive-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
This is a large benefit over enforcing segment adjacency.

There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons. 
Fig.~\ref{fig:skeleton-results} shows such an example segment that our algorithm missed. 
The endpoints of both segments are circled.
In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
	\caption{Example merge candidates.}
	\label{fig:skeleton-results}
\end{figure}

@@

Figure \ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all datasets.
%We train our CNN using one of the Kasthuri volumes and test using the other three datasets.
Since our CNN only takes as input a region of the label volume we can train on  anisotropic data and test on isotropic data.
This provides a major benefit given the time-intensive task of manually generating ground truth for each dataset at various resolutions.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{./figures/receiver-operating-characteristic.jpg}
	\caption{The receiver operating characteristic (ROC) curves of our CNN for all four datasets.}
	\label{fig:receiver-operating-characteristic}
\end{figure}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{c c c c} \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri Training & +3.60\% & -0.01\% & +0.60\% \\
		Kasthuri Testing & +7.59\% & -1.77\% & +1.38\% \\
		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% \\
		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% \\ \hline
	\end{tabular}
	\caption{Precision, recall, and accuracy changes between CNN only and graph-optimized reconstructions for the training and three test datasets.}
	\label{table:multicut}
\end{table}

>>>>

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-train-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-microns-test-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
	\includegraphics[width=0.45\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
	\caption{VI scores of our method (red) compared to the baseline segmentation (green) and an oracle (blue) that optimally partitions the graph based on ground truth. Lower scores are better. Our method improves the accuracy of the segmentation in all cases.}
	\label{fig:variation-of-information}
\end{figure*}

@@

We evaluate the performance of the different methods using variation of information (VI)~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over and undersegmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively. Since we are measuring the entropies between two clusterings, lower VI scores are better.

@@

Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \FIX{X\%} and only increasing the VI merge score by \FIX{X\%}.
Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
We see significant improvements on the Kasthuri datasets (VI split reduction of \FIX{X\%} and \FIX{X\%} on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \FIX{X\%} and \FIX{X\%}). This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.

Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol. 2 dataset. Several of these examples combine multiple consecutive segments that span the volume.
In the third example we correct the over-segmentation of a dendrite and attached spine-necks.
Fig.~\ref{fig:negative-results} shows typical failure cases of our method (red circles).
In two of these examples the algorithm correctly predicted several merges before a single error rendered the segment as wrong.
In the third example (blue circle) a merge error in the initial segmentation propagated to our output.
We now analyze how each major component of our method contributes to this final result.

@@

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:positive-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
This is a large benefit over enforcing segment adjacency.

There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons. 
Fig.~\ref{fig:skeleton-results} shows such a case. 
The endpoints of both segments are circled.
In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
	\caption{A false negative example of our method due graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
	\label{fig:skeleton-results}
\end{figure}

@@

Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all datasets.
%We train our CNN using one of the Kasthuri volumes and test using the other three datasets.
Since our CNN only takes as input a region of the label volume we can train on  anisotropic data and test on isotropic data.
This provides a major benefit given the time-intensive task of manually generating ground truth for each dataset at various resolutions.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{./figures/receiver-operating-characteristic.jpg}
	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume. The dashed blue line indicates better performance on the FlyEM datasets with retraining compared to without (solid blue).}
	\label{fig:receiver-operating-characteristic}
\end{figure}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{c c c c} \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri Training & +3.60\% & -0.01\% & +0.60\% \\
		Kasthuri Testing & +7.59\% & -1.77\% & +1.38\% \\
		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% \\
		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% \\ \hline
	\end{tabular}
	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets. The combined method results in better precision and accuracy.}
	\label{table:multicut}
\end{table}
